---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GuardianR

<!-- badges: start -->
<!-- badges: end -->

GuardianR provides an interface to the Open Platform's Content API of the Guardian Media Group. 
It retrieves content from news outlets The Observer, The Guardian, and guardian.co.uk from 1999 to current day.
See [CRAN](https://cran.r-project.org/web/packages/GuardianR/index.html) for the original package.

## About this fork

In this fork I changed a few things in the functions to make them compatible with my own work.


## Installation

You can install the released version of GuardianR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("GuardianR")
```

You can intall this fork from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JBGruber/GuardianR")
```
## Example

This is a basic example:

```{r example}
library("GuardianR")
results <- get_guardian(
  keywords = "Theresa May AND (Brexit OR EU)",
  from = "2019-01-16",
  to = "2019-01-30",
  api_key = "212d23d3-c7b2-4273-8f1b-289a0803ca4b"
)
results
```

